### 2021-12-19 documentos/kraus.tex
Updated framework to the lattest version
dandole

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$,
% \label{}
% \end{equation}
which in turn imply that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
\cpnote{This is the original $a$, not $H \otimes H$. See how to relate these
two matrices, or define a new $a$ and $A$} \ddnote{tengo entendido que nunca se define o redefine $a$ como $H \otimes H$, ni en el apendice, solo se dice que se intercambian para ciertos calculos. Creo que la notacion es segura.}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on an $N$ qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta}  \frac{1+A_{\vec \alpha \vec \beta}}{ 2} r_{\vec \beta} \sigma_{\vec \beta}
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel\ddnote{agrego 'channel', aqui el PCE map si es por construccion un canal}. Moreover, One can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the aforementioned channel is a PCEG.

@@

PCE channels can be seen as the fixed points of some decoherence process. We will show this first for PCEGs. Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha}.
\end{align}
It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process. The Lindblad generator~\cite{lindblad}, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.

Since PCEGs commute, we can construct easily decoherence processes for any other PCE channel, in these cases the Lindblad generator 
\begin{itemize}
\item Relate to decoherence, for PCEG
\item Play with non PCEG PCEs
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}

>>>>

We shall first show that the aforementioned Kraus operators indeed produce a PCE. 
Notice that 
% \begin{equation}
$\sigma_\alpha \sigma_\beta \sigma_\alpha =a_{\alpha \beta} \sigma_\beta$,
% \label{}
% \end{equation}
which in turn imply that 
\begin{equation}
\sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} 
=\san_{\vec \alpha \vec \beta} \sigma_{\vec \beta}.
\label{eq:sigma_property}
\end{equation}
\cpnote{This is the original $a$, not $H \otimes H$. See how to relate these
two matrices, or define a new $a$ and $A$} \ddnote{tengo entendido que nunca se define o redefine $a$ como $H \otimes H$, ni en el apendice, solo se dice que se intercambian para ciertos calculos. Creo que la notacion es segura.}
% with $a$ the matrix that appears in \eqref{eq:eigvals-PCE}. 
Next, consider the action of a channel with Kraus representation 
\eqref{eq:kraus:PCE} on an $N$ qubit system:
\begin{align}
\rho \mapsto &\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \left( \frac{1}{2} \sigma_{\vec \beta} + \frac{1}{2} \sigma_{\vec \alpha} \sigma_{\vec \beta} \sigma_{\vec \alpha} \right)\nonumber \\
=&\frac{1}{2^N}\sum_{\vec \beta} r_{\vec \beta} \frac{1+A_{\vec \alpha \vec \beta}}{ 2}\sigma_{\vec \beta}
\end{align}
However, since $\san_{\vec \alpha \vec \beta} = \pm 1$, the channel characterized
by Kraus operators  \eref{eq:kraus:PCE} is a PCE channel\ddnote{agrego 'channel', aqui el PCE map si es por construccion un canal}. Moreover, One can notice that, 
except for the first row, half of the matrix elements of each row is $+1$ and 
half $-1$, which implies that the aforementioned channel is a PCEG.

@@

PCE channels can be seen as the fixed points of some decoherence process. We will show this first for PCEGs. Consider the following dynamical process that \textit{implements} the PCEG $\mcG_{\vec \alpha}$ when $t\to \infty$,
\begin{align}
\mcG_{\vec \alpha,t}[\rho]&=e^{- \gamma t} \rho + (1-e^{-\gamma t})\mcG_{\vec \alpha}[\rho]\nonumber \\
&=\frac{\left( 1+e^{- \gamma t} \right)}{2} \rho +\frac{\left( 1-e^{- \gamma t} \right)}{2} \sigma_{\vec \alpha} \rho \sigma_{\vec \alpha},
\end{align}
where $\gamma>0$. It is easy to prove that the family of channels $\mcG_{\vec \alpha, t}$ parametrized with $t \geq 0$ forms a one-parametric semigroup, \ie{} $\mcG_{\vec \alpha, t_1}\mcG_{\vec \alpha, t_2}=\mcG_{\vec \alpha, t_1+t_2}$, therefore $\mcG_{\vec \alpha, t}$ describes a dissipative time-homogeneous Markovian process. The Lindblad generator~\cite{lindblad}, $\mcL_{\vec \alpha}$, can be obtained with the standard procedure,  
\begin{equation}
\mcL_{\vec \alpha}[\rho]=\left. \frac{d\mcG_{\vec \alpha,t}[\rho]}{dt}\right|_{t=0}=\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2},
\end{equation}
where the unique Lindblad operator associated with the relaxation ratio $\gamma/2$ is simply $\sigma_{\vec \alpha}$.

Since PCEGs commute, we can describe easily any other PCE channel as a fixed point of a decoherence process. For them, the Lindblad generator is simply the sum of the generators of the corresponding generators, thus, the Lindblad operators are simply [...] The channel depicted in [...] is equal to $\mcG_{(0,3)}\mcG_{(3,3)}$
\begin{equation}
\mcL=\frac{\gamma_{(0,3)}\left(\one\otimes\sigma_z\rho\one\otimes\sigma_z -\rho \right)}{2}+\frac{\gamma\left(\sigma_{\vec \alpha}\rho \sigma_{\vec \alpha} -\rho \right)}{2}
\end{equation}

In addition to decoherence processes, PCE channels can also be described with collision models, 
\begin{itemize}
\item Relate to decoherence, for PCEG
\item Play with non PCEG PCEs
\item Dependiendo de si sale algo bonito, podemos poner algun modelo en
particular para todos los canales (sistema central + ambiente). Seria de buscar
dilataciones sencillas y razonables por lo menos a los canales generadores.
\todo{Davalos lidera la discusión de ese punto, pero no escribe nada}
\end{itemize}
